---
title: "Milestone #3"
author: "Gayatri Balasubramanian"
date: "10/4/2019"
output: html_document
---

```{r setup, include=FALSE}

# default settings

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)


# download libraries we need

library(gt)
library(janitor)
library(tidyverse)

```

## Problem statement

I want to explore Census data on geographic distribution of ethnicity by county in Indiana, related to the distribution of industry in Indiana (such as retail, nails, eyebrows, massage, hair, farm, surgeons, dentistry, information technology, school, universities, manufacturing).


### Data obtained

I have data obtained from [Census Reporter]("censusreporter.org") that displays by Indiana county the population of each of the respective races: Caucasian, Black, Asian (broken down by subcategory), Pacific Islander (broken down by subcategory), Hispanic (broken down by subcategory), and Native American (broken down by subcategory). Limitations of this data are that the Census does not record Caucasion or Black subcategories, so European and African ethnicities are not recorded.


### Diplaying some data

```{r read_data}

# read table for each ethnicity

white  <- read_csv("raw-data/white_indiana_by_county.csv", skip = 1) %>%
  clean_names()
asian  <- read_csv("raw-data/white_indiana_by_county.csv", skip = 1) %>%
  clean_names()
hispanic  <- read_csv("raw-data/hispanic_indiana_by_county.csv", skip = 1) %>%
  clean_names()
indigenous  <- read_csv("raw-data/nativeamerican_indiana_by_county.csv", skip = 1) %>%
  clean_names()
black  <- read_csv("raw-data/black_indiana_by_county.csv", skip = 1) %>%
  clean_names()
pacific  <- read_csv("raw-data/pacificislander_indiana_by_county.csv", skip = 1) %>%
  clean_names()

# shorten tables for display

white_sample <- white %>% head(5)
asian_sample <- asian %>% head(5)
hispanic_sample <- hispanic %>% head(5)
indigenous_sample <- indigenous %>% head(5)
black_sample <- black %>% head(5)
pacific_sample <- pacific %>% head(5)

```


```{r gt_data}

# display white data in table as example

gt(data = white_sample) %>% 
  tab_header(
    title = "White",
    subtitle = "Indiana Census by County"
  )


```

Currently all the data per race looks similar to this.


### Plan for obtaining future data

I need to obtain the number of each industry per county. I plan to obtain this data thru Google maps, perhaps through webscraping unless I find an easier way to do it.  

I also need to clean up the data further by renaming columns to designate the columns as subcategories rather than census codes.


## Plans

1. Obtain industry data  
2. Plot race by county for each industry  
3. Create a visual color map showing county lines, industry info, and race info.