---
title: "Milestone #4"
author: "Gayatri Balasubramanian"
date: "10/10/2019"
output: html_document
---

```{r setup, include=FALSE}

# default settings

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)


# download libraries we need

library(janitor)
library(tidyverse)

```

### Problem statement

How does Census data on geographic distribution of ethnicity by county in Indiana related to the distribution of industry in Indiana?

### Graph and Progress

This week I went through my data and cleaned it up. It was a lot to clean up, but now I have every county and every subdivision of race provided by census reporter. I also decided to focus on the races: black, white, asian, native american, hispanic, and to leave out pacific islanders.


```{r first_plot}

# read table for all races

combined_race  <- read_csv("raw-data/all_races.csv") %>%
  clean_names()


# filter data for hamilton county, in only

hamilton_county <- combined_race %>% 
  select(ethnicity, race, hamilton_county_in) %>% 
  filter(hamilton_county_in != 0, race != "White") %>% 
  arrange(desc(hamilton_county_in))




```